---
title: "**Sample Markdown Document**"

author: "Madhur Bansal"

date: "2022-09-14"
output: html_document
--- 

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### **Welcome to this sample document**  

##### **Solving Quadratic equations**  


Consider the equations of the form $ax^{2} + bx + c = 0$. This is a quadratic equation; changing the values of $a$, $b$, and $c$ changes the shape of the quadratic. The two solutions to a quadratic equation:
$$
x = \dfrac{-b \pm \sqrt{b^{2} - 4ac}}{2a}
$$

Let's draw a quadratic curve for different values of $a$, $b$, and $c$.

```{r quadratic curve, fig.align = 'center'}
a <- 10
b <- 3
c <- -5
x <- seq(-2, 2, length = 1e3)
fx <- a*x^2 + b*x + c
plot(x, fx, type = 'l', xlab = "x", ylab = "Quadratic function")
#Ading a line for the solution
abline(h = 0, lty = 2, col = "red")
```

In the above, we can also change the way the plot appears. I will rerun the above code, without displaying the code, and only producing the plot of figure height "4" units and figure width "4" units

```{r quadratic curve shaped, echo = FALSE, fig.width = 4, fig.height = 4, fig.align = 'center', fig.cap = "Figure 1: A Quadratic function"}
a <- 10
b <- 3
c <- -5
x <- seq(-2, 2, length = 1e3)
fx <- a*x^2 + b*x + c
plot(x, fx, type = 'l', xlab = "x", ylab = "Quadratic function")
#Ading a line for the solution
abline(h = 0, lty = 2, col = "red")
```  

  
  
##### **Studying the Cricket Dataset**  

We will study the cricket dataset more closely now. The `battingbowling.csv` file in your repository contains information regarding various potential all-rounders in men’s ODI cricket. The players’ batting average, bowling average, and team is present in the dataset.